---
title: "Untitled"
author: "Rachel Sinondang"
date: "4/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse) # untuk transformasi data
library(plotly) # untuk membuat plot menjadi interaktif
library(glue) # untuk custom informasi saat plot interaktif
library(scales) # untuk custom keterangan axis atau lainnya
library(ggpubr) # untuk export plot
```

```{r}
placement <- read.csv("Placement_Data_Full_Class (1).csv")
```

ssc_p : Secondary Education percentage- 10th Grade  
ssc_b : Board of Education- Central/ Others  
hsc_p : Higher Secondary Education percentage- 12th Grade  
hsc_b : Board of Education- Central/ Others  
hsc_s : Specialization in Higher Secondary Education  
degree_p : Degree Percentage  
degree_t : Under Graduation(Degree type)- Field of degree education  
workex : Work Experience  
etest_p : Employability test percentage ( conducted by college)  
specialisation : Post Graduation(MBA)- Specialization  
mba_p : MBA percentage  

```{r}
p_status <- placement %>% select(-c(sl_no,salary)) %>%
  mutate(gender = as.factor(gender),
         ssc_b = as.factor(ssc_b),
         hsc_b = as.factor(hsc_b),
         hsc_s = as.factor(hsc_s),
         degree_t = as.factor(degree_t),
         workex = as.factor(workex),
         specialisation = as.factor(specialisation),
         status = as.factor(status)) %>%
  drop_na()
```

```{r}
RNGkind(sample.kind = "Rounding")
set.seed(100)

index <- sample(nrow(p_status), nrow(p_status) * 0.8)
status_train <- p_status[index,]
status_test <- p_status[-index,] 
```

```{r}
prop.table(table(status_train$status))
```


```{r message=F, eval=F}
library(randomForest)
library(caret)
RNGkind(sample.kind = "Rounding")
set.seed(100)

ctrl <- trainControl(method="repeatedcv", number = 7, repeats = 4)

model_forest <- train(status ~ ., data = status_train, method = "rf", trControl = ctrl)

saveRDS(model_forest, "model_forest.RDS") # simpan model
```

```{r}
library(randomForest)
model_forest$finalModel
```

```{r}
forest_class <- predict(model_forest, status_test, type = "raw")
head(forest_class)
```

```{r}
confusionMatrix(data = forest_class, reference = as.factor(status_test$status),positive = "Placed")
```
```{r}
p_status %>%
  filter(status == "Placed") %>%
  group_by(hsc_s) %>%
    summarise(total = n())
```

```{r}
p_status %>%
  filter(status == "Placed") %>%
  group_by(hsc_s) %>%
  summarise(rerata = mean(ssc_p))
```
```{r}
p_status %>%
  filter(status == "Placed") %>%
  group_by(hsc_s) %>%
  summarise(rerata = mean(hsc_p))
```
```{r}
p_status %>%
  filter(status == "Placed") %>%
  group_by(hsc_s) %>%
  summarise(rerata = mean(degree_p))
```
```{r}
p_status %>%
  filter(status == "Placed") %>%
  group_by(hsc_s) %>%
  summarise(rerata = mean(etest_p))
```

```{r}
p_status %>%
  filter(status == "Placed",
         specialisation == "Mkt&Fin") %>%
  group_by(hsc_s) %>%
  summarise(rerata = mean(mba_p))
```

```{r}
by_gen <- p_status %>%
  filter(status == "Placed", specialisation == "Mkt&Fin") %>%
  group_by(gender, hsc_s) %>%
  summarise(total = n())


```


```{r}
per <- by_gen %>%
  group_by(hsc_s) %>% 
  mutate(proportion = round(total/sum(total),2)*100)
```

```{r}
theme_algoritma <- theme(legend.key = element_rect(fill="black"),
           legend.background = element_rect(color="white", fill="#263238"),
           plot.subtitle = element_text(size=6, color="white"),
           panel.background = element_rect(fill="#dddddd"),
           panel.border = element_rect(fill=NA),
           panel.grid.minor.x = element_blank(),
           panel.grid.major.x = element_blank(),
           panel.grid.major.y = element_line(color="darkgrey", linetype=2),
           panel.grid.minor.y = element_blank(),
           plot.background = element_rect(fill="#263238"),
           text = element_text(color="white"),
           axis.text = element_text(color="white")
           
           )
```

```{r}
library(plotly)
library(ggplot2)

plot_composition <- per %>% 
  ggplot(aes(x = total, 
             y = hsc_s,
             text = glue("Gender: {gender}
                         Proportion: {proportion}%"))) +
  geom_col(aes(fill = gender), position = "fill") +
  geom_vline(xintercept = 0.5, col = "white", lty = 2, lwd = 1.5) + #membuat vertical line
  labs(title = "Composition of Male and Female",
       x = NULL,
       y = NULL) +
  scale_fill_manual(values = c("black", "firebrick")) +
  scale_y_discrete(labels = wrap_format(30)) + # wrap tulisan agar tidak terlalu panjang
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  theme_algoritma + #harus dirun chunk atas untuk custom theme yg disediakan
  theme(legend.position = "none") #untuk hapus legend
```


```{r}
```


```{r}
ggplotly(plot_composition, tooltip = "text")
```

Which factor influenced a candidate in getting placed?
Does percentage matters for one to get placed?
Which degree specialization is much demanded by corporate?
Play with the data conducting all statistical tests.
